% @Author: ArthurBernard
% @Email: arthur.bernard.92@gmail.com
% @Date: 2019-07-31 22:09:26
% @Last modified by: ArthurBernard
% @Last modified time: 2019-08-04 17:52:06
\documentclass[a4paper]{arthur-cv}
\title{Curiculum Vitae}
\author{Arthur Bernard}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{xcolor}

% Customize colorthem
% \definecolor{leftcolorband}{HTML}{e0e0e0}
% \definecolor{boxcolor}{HTML}{851919}
% \definecolor{maincolor}{HTML}{420c0c}
% \definecolor{secondcolor}{HTML}{861919}
% \definecolor{thirdcolor}{HTML}{591111}

% Define color for hyperlink
\definecolor{colhyperlink}{HTML}{0E5484}

% Set profile info
\profilepic{}
\cvname{Arthur Bernard}
\cvlinkedin{/in/arthur-bernard-789955152}
\cvgithub{ArthurBernard}
\cvmail{arthur.bernard.92@gmail.com}
\cvnumberphone{+33 6 59 29 14 50}
\cvjobtitle{Data Scientist in Quantitative Finance}
\cvsite{}
\cvaddress{}
\cvyearsold{}

\begin{document}
\makeprofile % Set header

\begin{textblock}{20.5}(0.25, 3.5)

  \begin{minipage}[t]{0.37\textwidth}

    %%%%%%%%%%%%%%%%%
    %%  Left side  %%
    %%%%%%%%%%%%%%%%%

    \sectionleft{Key skills}
      \subsectionleft{Proficiency in \textbf{statistics} \& \textbf{econometrics softwares}:}{R (Advanced), Octave/Matlab (Advanced), SAS (Beginner), STATA (Beginner).}

      \subsectionleft{Operating systems:}{\textbf{Unix} and \textbf{Windows}.}

      \subsectionleft{Languages:}{French (\textbf{native speaker}), English (\textbf{professional skill}).}

      \subsectionleft{Database:}{Basic knowledges with \textbf{SQL} and \textbf{NoSQL} database.}

    \sectionleft{Programming}
      \subsectionleft{Highly advanced:}{\textbf{Python} (expertise in NumPy, Pandas, Cython, PyTorch, Keras, Sickit-Learn, Asyncio, Multi-process/thread, etc).}

      \subsectionleft{Advanced:}{\textbf{Shell}, VBA, \LaTeX.}

      \subsectionleft{In progress:}{\textbf{C++}.}
  
    \sectionleft{MOOC's}
      \subsectionleft{Learn to program with \textbf{Python},}{on OpenClassRooms.}

      \subsectionleft{\textbf{Machine Learning}, by Andrew Ng,}{on Coursera.}

      \subsectionleft{\textbf{Deep Learning}, by Andrew Ng,}{on Coursera.}

      \subsectionleft{And other diverse courses (\textbf{Linux}, \textbf{C++}, etc.).}{}

    \sectionleft{Interests}
      \subsectionleft{Artificial intelligence.}{}

      \subsectionleft{Crypto-currencies/Blockchains.}{}

  \end{minipage}\hfill\begin{minipage}[t]{0.61\textwidth}

    %%%%%%%%%%%%%%%%%%
    %%  Right side  %%
    %%%%%%%%%%%%%%%%%%
  
    \section{Experiences}
      \begin{rightenv}
        \subsectionright{Jan. 2019 – Present}{Quant Researcher}[at \textbf{Napoleon Group}][Paris]{R\&D of trading strategies, \textbf{multivariate prediction} with neural networks, \textbf{execution order algorithms}, development of \textbf{backtesting} and \textbf{financial analysis} tools, and webscraping data.}

        \subsectionright{Jun. 2018 – Dec. 2018}{Intern in Quantitative Finance}[at \textbf{Napoleon Group}][Paris]{Research of quantitative strategies and \textbf{portfolio allocation} algorithms. \textbf{Data-science competition} elaborated for the Collège de France.}

        \subsectionright{Sept. 2013 – May 2018}{Director}[at \textbf{Mutuelle des Etudiants de Provence}][Marseille]{Approval of budgets, financial investments, internal policy, etc.}
      \end{rightenv}

    \section{Personal projects}
      \begin{rightenv}
        \subsectionright{2018 – 2019}{Machine/deep learning tools adapted to finance}{Development of a python and cython package to create \textbf{neural networks}, \textbf{backtest strategies}, analysis with \textbf{econmetric models} and \textbf{financial indicators}, etc. Published on PyPI as \href{https://github.com/ArthurBernard/Fynance}{\textcolor{colhyperlink}{\textit{fynance}}}.}

        \subsectionright{2017 – 2018}{Webscraping package}{Development of a python package to \textbf{download data} and \textbf{update database} from some crypto-currency's exchanges. Published on PyPI as \href{https://github.com/ArthurBernard/Download_Crypto_Currencies_Data}{\textcolor{colhyperlink}{\textit{dccd}}}.}

        \subsectionright{2016 – 2019}{Trading bot algorithms on crypto-currencies}{Development and maintenance of trading bots with python and bash scripts. Starting in 2016 with \textbf{arbitrage strategy}, and more recently create \textbf{strategies with neural network}. A part is available on my GitHub in the repository \href{https://github.com/ArthurBernard/Strategy_Manager}{\textcolor{colhyperlink}{\textit{Strategy\_Manager}}}.}
      \end{rightenv}

    \section{Education}
      \begin{rightenv}
        \subsectionright{2017 – 2018}[Master's Degree]{Econometrics of Banking and Financial markets}[at \textbf{Aix-Marseille School of Economics}][Marseille]{\textbf{Courses:} Stochastic finance, financial econometrics, financial engineering, econometrics of exchange rates, neural network, etc.\\\textbf{Projects:} Intraday analysis of BTCUSD versus EURUSD, etc.\\\textbf{Master thesis:} Analysis of dynamics of Bitcoin.}

        \subsectionright{2013 – 2016}[Bachelor's degree]{Economics and Management}[at \textbf{Aix-Marseille University}][Marseille]{\textbf{Specialization:} Finance.\\\textbf{Courses:} Time series econometrics, financial markets, statistics, optimization, informatic (SQL and VBA), etc.}

        \subsectionright{2012}[A-Level]{Science}[at \textbf{High-School M. M. Fourcade}][Gardanne]{}
      \end{rightenv}

    \section{Miscellaneous}
      \begin{rightenv}
        \subsectionright{2019}{Data-science competition}[at \textbf{ENS Challenge Data}]{$7^{th}$ out of more than 70 candidates in the temporary ranking, about prediction of daily stock movements on the US market, proposed by Capital Fund Management.}

        \subsectionright{2014 – 2016}{Founder and general secretary of student association}{Organisation and management of team projects.}

        \subsectionright{Present}{Hobbies}{Cooking, travelling (Norway, Scotland, Eastern countries, etc.), swimming (competition) and theater.}
      \end{rightenv}

  \end{minipage}

\end{textblock}

\end{document}
