% @Author: ArthurBernard
% @Email: arthur.bernard.92@gmail.com
% @Date: 2019-07-02 19:18:05
% @Last modified by: ArthurBernard
% @Last modified time: 2019-07-09 08:54:57
\documentclass[a4paper]{arthur-cv-en}
\title{Curiculum Vitae}
\author{Arthur Bernard}

\usepackage[english]{babel}
\usepackage{fontspec}

% Set profile info
\cvname{Arthur Bernard}
\cvlinkedin{/in/arthur-bernard-789955152}
\cvgithub{ArthurBernard}
\cvmail{arthur.bernard.92@gmail.com}
\cvnumberphone{+33 6 59 29 14 50}
\cvaddress{7, Rue des Innocents, Paris, 75001}
\cvjobtitle{Data Scientist in Quantitative Finance}
%\cvsite{}

\begin{document}
\makeprofile % Set header

\begin{textblock}{20.5}(0.25, 3.5)

  \begin{minipage}[t]{0.37\textwidth}

    %%%%%%%%%%%%%%%%%
    %%  Left side  %%
    %%%%%%%%%%%%%%%%%

    \sectionleft{Key skills}
      \subsectionleft{Proficiency in statistics and econometrics softwares:}{Octave/Matlab (Advanced), R (Advanced), SAS (Beginner), STATA (Beginner).}
      \subsectionleft{Operating system:}{Windows and Unix.}
      \subsectionleft{Languages:}{French (native speaker), English (professional skill, langage of instruction of Master 1 and 2).}

    \sectionleft{MOOC's}
      \subsectionleft{Learn to program with \textbf{Python},}{OpenClassRooms.}
      \subsectionleft{\textbf{Machine learning}, by Andrew Ng,}{Coursera.}
      \subsectionleft{\textbf{Deep learning}, by Andrew Ng,}{Coursera.}
      \subsectionleft{And other diverse courses (\textbf{Linux}, \textbf{C++}, etc.).}{}

    \sectionleft{Programming}
      \subsectionleft{Highly advanced:}{Python (proficiency NumPy, Pandas, Cython, PyTorch, Keras, Sickit-Learn, Asyncio, Multi-process/thread), etc.}
      \subsectionleft{Advanced:}{Shell, VBA, Matlab/Octave, LaTeX.}
      \subsectionleft{In progress:}{C++}
      \subsectionleft{Some notions:}{R, SAS}
      %\subsectionleft{Python}{Highly advanced: Asynchronous, Cython, NumPy, Pandas, Sickit-learn, PyTorch, Multi-process/thread etc.}
      %\subsectionleft{VBA}{Advanced.}
      %\subsectionleft{C++}{Beginner.}

    \sectionleft{Interests}
      \subsectionleft{Artificial intelligence.}{}
      \subsectionleft{Crypto-currencies/Blockchains.}{}

  \end{minipage}\hfill\begin{minipage}[t]{0.61\textwidth}

    %%%%%%%%%%%%%%%%%%
    %%  Right side  %%
    %%%%%%%%%%%%%%%%%%
  
    \section{Experiences}
      \begin{rightenv}
        \subsectionright{Jan. 2019 – Present}{Research in Quantitative Finance}[Napoleon Crypto][Paris]{R\&D of trading strategies using neural networks to \textbf{multivariate prediction}, \textbf{execution order algorithms}, development of \textbf{backtesting} and \textbf{financial analysi}s tools, and webscraping data.}
        \subsectionright{Jun. 2018 – Dec. 2018}{Intern in Quantitative Finance}[Napoleon Crypto][Paris]{Research of quantitative strategies and \textbf{portfolio allocation} algorithms and creation of a \textbf{data-science competition} proposed to the Collège de France.}
        \subsectionright{Sept. 2013 – May 2018}{Administrator (volunteer)}[Mutuelle des Etudiants de Provence][Marseille]{Approval of budgets, financial investments, internal policy, etc.}
      \end{rightenv}

    \section{Personal projects}
      \begin{rightenv}
        \subsectionright{2018 – 2019}{Machine/deep learning tools adapted to finance}{Development of python and cython package to create \textbf{neural networks}, \textbf{backtest strategies}, analysis with \textbf{econmetric models} and \textbf{financial indicators}, etc. Published on PyPI as \textit{fynance}.}
        \subsectionright{2017 – 2018}{Webscraping package}{Development of a python package to \textbf{download data} and \textbf{update database} from some crypto-currency's exchanges. Published on PyPI as \textit{dccd}.}
        \subsectionright{2016 – 2019}{Trading bot algorithms on crypto currencies}{Development and maintenance of trading bots with python and bash scripts. Starting in 2016 with \textbf{arbitrage strategy}, and more recently create \textbf{strategies with neural network}. A part is available on my GitHub in the repository \textit{Strategy\_Manager}.}
      \end{rightenv}

    \section{Education}
      \begin{rightenv}
        \subsectionright{2017 – 2018}[Master's Degree]{Econometrics of Banking and Financial markets}[Aix-Marseille School of Economics][Marseille]{\textbf{Courses:} Stochastic finance, financial econometrics, financial engineering, econometrics of exchange eates, neural network, etc.\\\textbf{Projects:} Intraday analysis of BTCUSD versus EURUSD, etc.\\\textbf{Master thesis:} Analysis of dynamics of Bitcoin.}
        \subsectionright{2013 – 2016}[Bachelor's degree]{Economics and Management}[Aix-Marseille Université][Marseille]{\textbf{Specialization:} Finance.\\\textbf{Courses:} Time series econometrics, financial markets, statistics, optimization, informatic (SQL and VBA), etc.}
        \subsectionright{2012}[A-Level]{Science}[High-School Marie Madeleine Fourcade][Gardanne]{}
      \end{rightenv}

    \section{Miscellaneous}
      \begin{rightenv}
        \subsectionright{2019}{Data-science competition}[ENS Challenge Data]{$7^{th}$ in the temporary ranking, about prediction of daily stock movements on the US market, proposed by Capital Fund Management.}
        \subsectionright{2014 – 2016}{Founder and general secretary of student association}{Organisation and management of team projects.}
        \subsectionright{Present}{Hobbies}{Cooking, travelling (Norway, Scotland, Eastern countries, etc.), swimming (competition) and theater.}
      \end{rightenv}

  \end{minipage}

\end{textblock}

\end{document}
